%--- Part 1: Motivation (4 min) -------------------------------------------------

\section{Motivation}

%--- Slide: Trajectory Prediction for Autonomous Driving -----------------------
\begin{frame}{Trajectory Prediction for Autonomous Driving}
  \begin{columns}
    \begin{column}{0.55\textwidth}
      \textbf{Task:} forecast the future $(x, y)$ positions of surrounding
      agents---pedestrians, cyclists, vehicles---from their observed past
      movements.
      \vspace{0.5em}
      \begin{itemize}[<+->]
        \item Essential for \emph{safe path planning} and collision avoidance
              in autonomous vehicles
        \item Inherently \emph{multimodal}: many plausible futures exist
              (a pedestrian may turn left or right)
        \item Agents \emph{interact} with each other and react to the
              scene layout
        \item Scene context matters: open squares behave very differently
              from narrow corridors
      \end{itemize}
    \end{column}
    \begin{column}{0.42\textwidth}
      \vspace{0.5em}
      \begin{center}
        % TODO: replace with a trajectory prediction figure (e.g. nuScenes scene
        % with predicted trajectories overlaid)
        \textit{[figure placeholder]}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

%--- Slide: Federated Learning for Trajectory Prediction ----------------------
\begin{frame}{Federated Learning for Trajectory Prediction}
  \begin{columns}
    \begin{column}{0.54\textwidth}
      \textbf{What is Federated Learning?}\\[0.3em]
      Train a shared model across many clients (cameras, cities, operators)
      \emph{without moving raw data}---clients share model updates, not video.
      \vspace{0.5em}
      \begin{itemize}[<+->]
        \item Video data is privacy-sensitive and cannot be centralized
        \item Trajectory data is naturally distributed across many sites
        \item Each site has \emph{unique motion patterns} (non-IID):
              a single global model may not fit all environments
        \item \textbf{Personalization:} share a common encoder, keep
              local prediction heads per site
      \end{itemize}
    \end{column}
    \begin{column}{0.43\textwidth}
      \onslide<2->{
      \textbf{Pipeline:}\\[0.4em]
      \small
      \begin{tabular}{l}
        Video stream \\
        $\downarrow$ Detection \& Tracking \\
        $\downarrow$ Trajectories $(x, y, t)$ \\
        $\downarrow$ Local model training \\
        $\downarrow$ Server aggregation \\
        $\downarrow$ Personalised prediction
      \end{tabular}
      }
    \end{column}
  \end{columns}
\end{frame}

%--- Slide: Research Questions -------------------------------------------------
\begin{frame}{The Problem with Aggregate Metrics}
  \begin{columns}
    \begin{column}{0.52\textwidth}
      Before scaling to FL, we need to understand model behaviour
      on a single dataset.
      \vspace{0.4em}
      \begin{itemize}[<+->]
        \item A single average ADE/FDE hides large variation across trajectories
        \item Some trajectories are inherently hard, others trivially
              easy---but \emph{why?}
        \item No understanding of which trajectory or scene characteristics
              drive per-trajectory prediction error
      \end{itemize}
      \vspace{0.5em}
      \onslide<4->{$\Rightarrow$ Aggregate metrics cannot guide personalisation
      decisions in FL.}
    \end{column}
    \begin{column}{0.45\textwidth}
      \onslide<5->{\textbf{Three Research Questions:}}
      \begin{enumerate}
        \item<5-> Which trajectory and scene characteristics affect model
              performance?
        \item<6-> Do distinct \emph{performance regimes} (recurring failure /
              success patterns) exist?
        \item<7-> How do model settings (history window, prediction horizon,
              attention radius) affect performance?
      \end{enumerate}
    \end{column}
  \end{columns}
\end{frame}
